Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-24 paper.qmd
Updated Figure 11 (b)

nldr_two_curvilinear_clust2 <- umap_two_curvilinear_clust |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("b") +
  theme(aspect.ratio = 1)

>>>>

nldr_two_curvilinear_clust2 <- umap_two_curvilinear_clust |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("b", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)
